---
title: "TFM Perceived Polarization"
author: "Chih-Hsuan Chang"
format: html
editor: visual
---

## Library

```{r lib, message=FALSE, warning=FALSE}
# data cleaning and table format
library(readr)
library(tidyverse)
library(gtsummary)
library(flextable)
library(Hmisc)
library(jtools) # cor-plot

# survey design
library(survey)
library(car)
library(srvyr)
library(svyVGAM)

# weighted correlation matrix
library(fastDummies)
library(weights)
library(ggcorrplot)

# table presentation
library(texreg)
library(modelsummary)
```

## Import Data

```{r import, warning=FALSE}
tcs24 <- read_csv("data.csv")
```

## Clean Data

```{r clean-data}
data <- tcs24 |> 
  dplyr::select(sel_gen, age, edugp, vo1, vo5,
                vk1m01, vk2m01:vk2m03, vk2m07:vk2m09, vk2m11, vk3m01,
                vj4_1:vj4_5,
                vjb2m01,
                wr_report) |> 
  rename(gender = sel_gen, edu = edugp, employ = vo1, income = vo5,
         line = vk1m01, fb = vk2m01, ig = vk2m02, x = vk2m03, tiktok = vk2m07,
         dcard = vk2m08, ptt = vk2m09, threads = vk2m11, youtube = vk3m01,
         polarization = vjb2m01,
         t_tvn = vj4_1, t_papern = vj4_2, t_broadcastn = vj4_3, t_magn = vj4_4,
         t_onlinen = vj4_5
         ) |> 
  mutate(
    age = case_when(
      age == 998 ~ NA,
      TRUE ~ age
    ),
    gender = case_when(
      gender == 1 ~ "male",
      gender == 2 ~ "female",
      TRUE ~ NA
    ),
    gender = factor(gender, levels = c("male", "female")),
    edu = case_when(
      edu %in% c(1, 2) ~ "low",
      edu %in% c(3, 4) ~ "medium",
      edu %in% c(5, 6) ~ "high", # college and graduate school
      TRUE ~ NA
    ),
    edu = factor(edu, levels = c("low", "medium", "high"), ordered = FALSE),
    employ = case_when(
      employ %in% c(1:5) ~ "employed",
      employ %in% c(7, 8) ~ "studying",
      employ %in% c(6, 11:13) ~ "unemployed",
      employ == 9 ~ "retired",
      employ == 10 ~ "homemaker",
      TRUE ~ NA
    ),
    employ = factor(employ, levels = c(
      "employed", "studying", "retired", "homemaker", "unemployed")),
    income = case_when(
      income %in% c(1:23) ~ income,
      TRUE ~ NA
    ),
    polarization = replace(polarization, polarization %in% 96:99, "NA"),
    polarization = factor(polarization,
                          levels = c(0, 1)
    ),
    across(line:youtube, as.factor),
    t_tvn = case_when(
      t_tvn %in% c(9999, 998, 997, 9996) ~ NA,
      TRUE ~ t_tvn
    ), 
    t_papern = case_when(
      t_papern %in% c(9999, 998, 997, 9996) ~ NA,
      TRUE ~ t_papern
    ), 
    t_broadcastn = case_when(
      t_broadcastn %in% c(9999, 998, 997, 9996) ~ NA,
      TRUE ~ t_broadcastn
    ), 
    t_magn = case_when(
      t_magn %in% c(9999, 998, 997, 9996) ~ NA,
      TRUE ~ t_magn
    ), 
    t_onlinen = case_when(
      t_onlinen %in% c(9999, 998, 997, 9996) ~ NA,
      TRUE ~ t_onlinen
    ), 
    across(t_tvn:t_onlinen, as.numeric),
    )
```

```{r income_quantile}
df <- data %>%
  mutate(income_num = as.numeric(income))

weighted_cuts <- wtd.quantile(
  df$income, 
  weights = df$wr_report, 
  probs = seq(0, 1, by = 0.25)
)

df <- df %>%
  mutate(
    income_quantile = cut(
      income_num, 
      breaks = weighted_cuts, 
      include.lowest = TRUE,
      # Add clear, descriptive labels for your model output
      labels = c(1:4)
    ),
    # Ensure it is an ordered factor for multiple imputation and regression
    income_quantile = factor(income_quantile, ordered = FALSE)
  ) %>%
  select(-income_num) # Clean up the temporary numeric column

data$income_quantile <- df$income_quantile
data <- data |> 
  select(-income) |> 
  relocate(income_quantile, .before = line)
```

## Create Platform Breadth

```{r platform-breadth}
platform_vars <- c("line", "fb", "ig", "x", "tiktok", "dcard", "ptt", "threads",  "youtube")
data <- data |> 
  mutate(dplyr::across(
    dplyr::all_of(platform_vars), 
    ~ as.numeric(as.character(.))
  )) |> 
  rowwise() |> 
  mutate(
    breadth = sum(dplyr::c_across(dplyr::all_of(platform_vars)))
  ) %>%
  ungroup()
```

## Explore the Data

### correlation matrix

```{r cor-matrix}
# 1. Create dummy variables for your categorical columns
# This splits your nominal variables while leaving numeric/binary variables untouched
matrix_data <- dummy_cols(
  data |> drop_na(), 
  select_columns = c("edu", "employ", "gender", "income_quantile"), # Specify your nominal variables here
  remove_selected_columns = TRUE # Removes the original text-based column
)

# 2. Subset the data to only the variables you want in the matrix
# Ensure ordinal variables (like education) are coded as numeric (e.g., 1, 2, 3)
vars_for_matrix <- matrix_data %>%
  drop_na() |> 
  dplyr::select(age, starts_with(c("edu_", "gender_", "employ_", "income_quantile_")),
         line, fb, ig, x, tiktok, dcard, ptt, threads, youtube,
         polarization, t_tvn, t_papern, t_broadcastn, t_magn, t_onlinen, wr_report) |> 
  mutate(across(everything(), ~ as.numeric(as.character(.))))

svy_matrix_design <- svydesign(
  ids = ~1, 
  weights = ~wr_report, 
  data = vars_for_matrix,
  na.rm = TRUE
)

# 3. Use svycor with na.rm = TRUE 
# This handles the weights AND does safe pairwise deletion for your NAs automatically
# Note: svycor automatically correlates all numeric variables in the design object
final_matrix <- svycor(~ age + gender_female + edu_low + edu_medium + edu_high + employ_homemaker + employ_studying + employ_unemployed + employ_retired + employ_employed + income_quantile_1 + income_quantile_2 + income_quantile_3 + income_quantile_4 + fb + ig + x + tiktok + dcard + ptt + threads + youtube + t_tvn + t_papern + t_broadcastn + t_magn + t_onlinen + polarization, design = svy_matrix_design, sig.stats = TRUE)
```

```{r cor-plot, warning=FALSE}
# 1. Extract the actual correlation matrix from the svycor object
cor_matrix <- final_matrix$cor

# 2. Extract the p-values so we can mark non-significant correlations
p_matrix <- final_matrix$p

# 3. Generate the Heatmap
corplot <- 
  ggcorrplot(
  cor_matrix,
  method = "square",       # Shape of the heatmap cells (can also be "circle")
  type = "lower",          # Only show the bottom half to avoid visual duplication
  lab = TRUE,              # Prints the actual correlation numbers inside the squares
  lab_size = 2,            # Adjust text size to prevent overlapping if you have many variables
  p.mat = p_matrix,        # Feed in the p-values
  sig.level = 0.05,        # Set your significance threshold
  insig = "blank",         # "blank" hides insignificant squares, "pch" puts an X over them
  colors = c("#6D9EC1", "white", "#E46726"), # Classic blue (negative) to red (positive) gradient
  title = "Weighted Correlation Matrix",
  legend.title = "Correlation\nCoefficient"
)
print(corplot)

#ggsave("correlation heatmap.jpg", corplot, width = 12, height = 12, dpi = 300)
```

### NA values

```{r na-table}
na_summary <- data |> 
  # Calculate ratio of NAs for every column
  summarise(across(everything(), ~ mean(is.na(.)))) |> 
  pivot_longer(
    cols = everything(), 
    names_to = "Column_Name", 
    values_to = "NA_Ratio"
  ) |> 
  arrange(desc(NA_Ratio))
```

```{r na-pattern}
gg_miss_var(data, show_pct = TRUE) +
  theme_minimal() +
  labs(
    title = "Percentage of Missing Data by Variable",
  )

gg_miss_fct(x = data, fct = polarization)
gg_miss_fct(x = data, fct = breadth)
na_breadth <- gg_miss_fct(x = data, fct = breadth)
gg_miss_case(x = data)
#ggsave("fct_NA in breadth.jpg", na_breadth, width = 12, height = 10, dpi = 300)
```

## Prepare Data

### breadth data

```{r lwd-data}
lwd_data <- data |> drop_na()

lwd_data
```

### repertoire data

```{r repertoire}
lwd_data_rep <- lwd_data %>%
  rowwise() %>%
  mutate(
    rep_label = paste(platform_vars[dplyr::c_across(dplyr::all_of(platform_vars)) == 1], collapse = " + ")
  ) %>%
  group_by(rep_label) %>%
  filter(sum(wr_report) >= 20) %>%
  ungroup()

lwd_data_rep
```

## Survey Design

### breadth design

```{r svy-breadth}
svy_breadth <- svydesign(
  ids     = ~1,           
  strata  = NULL,         
  weights = ~wr_report,   
  data    = lwd_data,
  nest    = FALSE
)
```

### repertoire design

```{r svy-rep}
svy_rep <- svydesign(
  ids     = ~1,           
  strata  = NULL,         
  weights = ~wr_report,   
  data    = lwd_data_rep,
  nest    = FALSE
)
```

## Descriptive Statistics

### breadth descriptive

```{r ds-breadth}
svymean(~ breadth + age + gender + edu + employ + income_quantile + t_tvn + t_papern + t_broadcastn + t_magn + t_onlinen + polarization,
        design = svy_breadth, na.rm = TRUE)

svysd(~ breadth + age + t_tvn + t_papern + t_broadcastn + t_magn + t_onlinen, design = svy_breadth, na.rm = TRUE)
```

### repertoire descriptive statistic

```{r ds-rep}
ds_table_rep <- lwd_data_rep |> 
  tbl_summary(
    statistic = list(all_continuous() ~ "{mean} ({sd})",
                     all_categorical() ~ "{n} ({p}%)"),
    missing = "always", # Shows missing data counts/percentages!
    missing_text = "missing data"
  ) |> 
  bold_labels() |> 
  as_flex_table() |> 
  # 3. Use flextable to make it APA style and save to Word
  flextable::theme_apa() |> 
  flextable::autofit()

# flextable::save_as_image(path = "outputs/table1_apa.docx")

svymean(~ rep_label + age + gender + edu + employ + income_quantile + t_tvn + t_papern + t_broadcastn + t_magn + t_onlinen + polarization,
        design = svy_rep, na.rm = TRUE)
```

## Constructing Models

### just breadth model

```{r base_model}
model_1 <- svyglm(polarization ~ breadth, family = quasibinomial(), design = svy_breadth)
```

### with demographic model

```{r base_model}
model_2 <- svyglm(polarization ~ age + gender + edu + employ + income_quantile + breadth, family = quasibinomial(), design = svy_breadth)
```

### trust in news media model

```{r}
model_3 <- svyglm(polarization ~ age + gender + edu + employ + income_quantile + t_tvn + t_papern + t_broadcastn + t_magn + t_onlinen + breadth, family = quasibinomial(), design = svy_breadth)
```

### individual platform model

```{r}
model_5 <- svyglm(polarization ~ age + gender + edu + employ + income_quantile + t_tvn + t_papern + t_broadcastn + t_magn + t_onlinen + line + fb + ig + x + tiktok + dcard + ptt + threads+ youtube, family = quasibinomial(), design = svy_rep)
```

### repertoire model

```{r rep_model}
model_4 <- svyglm(polarization ~ age + gender + edu + employ + income_quantile + t_tvn + t_papern + t_broadcastn + t_magn + t_onlinen + rep_label, family = quasibinomial(), design = svy_rep)
```

## Model Summary

**Estimator and p values**

```{r breadth-model-sum, warning=FALSE}
modelsummary(
  list(
    "Demogrphic Variables" = demo_model,
    "Trust in News Media" = trust_model,
    "Platform Breadth" = breadth_model,
    "Social Media Repertoir" = rep_model),
  exponentiate = TRUE,
  statistic = "({std.error})",
  stars = c('*' = .05, '**' = .01, '***' = .001),
  title = "Logistic Regression Results: Perceived Polarization (Odds Ratios)",
  output = "latex"
)
```

```{r rep-model-sum, warning=FALSE}
coef_first_half <- c("age", "genderfemale", "edumedium", "eduhigh", 
                     "employstudying", "employretired", "employhomemaker",
                     "employunemployed", "income_quantile2", "income_quantile3",
                     "income_quantile4", "t_tvn", "t_papern", "t_broadcastn", "t_magn",
                     "t_onlinen") # first half of vars
coef_second_half <- c("rep_labelline + fb", 
                      "rep_labelline + fb + ig",
                      "rep_labelline + fb + youtube",
                      "rep_labelline + ig + youtube",
                      "rep_labelline + fb + ig + youtube",
                      "rep_labelline + fb + ig + tiktok + youtube",
                      "rep_labelline + fb + ig + dcard + youtube",
                      "rep_labelline + fb + ig + threads + youtube",
                      "rep_labelline + fb + ig + dcard + threads + youtube",
                      "rep_labelline + fb + ig + tiktok + threads + youtube",
                      "rep_labelline + fb + ig + tiktok + dcard + threads + youtube",
                      "rep_labelline + youtub") # remaining vars

modelsummary(
  list(
    "Social Media Repertoire" = rep_model),
  exponentiate = TRUE,
  statistic = "({std.error})",
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = coef_first_half,
  gof_omit = ".*",  # omit fit stats from first half
  output = "latex"
)

modelsummary(
  list(
    "Social Media Repertoire" = rep_model),
  exponentiate = TRUE,
  statistic = "({std.error})",
  stars = c('*' = .05, '**' = .01, '***' = .001),
  coef_map = coef_second_half,
  title = NULL,  # no title on second half
  output = "latex"
)
```

**Confidence Interval**

```{r}
# options(knitr.table.format = "latex") 
first_table <- list(
  "Model 1 (Base)" = model_1,
  "Model 2 (Demographics)" = model_2,
  "Model 3 (Trust in News)" = model_3
)
sec_table <- list(
  "Model 4 (Repertoire)" = model_4,
  "Model 5 (Individual Platform)" = model_5
)

table_1 <- modelsummary(
  first_table,
  output = "t1.html",
  exponentiate = TRUE,
  estimate = "{estimate} [{conf.low}, {conf.high}]",
  statistic = NULL,
  conf_level = 0.95,
  gof_omit = "IC|Log.Lik|F|RMSE"
  )

table_2 <- modelsummary(
  sec_table,
  title = "Binary Logistic Reggression Models: Online Perceived Polarization",
  output = "t2.html",
  exponentiate = TRUE,
  estimate = "{estimate} [{conf.low}, {conf.high}]",
  statistic = NULL,
  conf_level = 0.95,
  gof_omit = "IC|Log.Lik|F|RMSE"
  )
```
